\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-08-22 evaluation.tex
added a draft table with stats
draft results table
added cite to Paul's paper

Benchmarks that are not production code (e.g. multipaxos) that can be used to evaluate testing

@@

\subsection{Stressing testing vs Systematic testing}

@@

>>>>

\newcommand{\colspacing}{\hspace{1.8em}}
\begin{table}[t]
\small
\centering
\setlength{\tabcolsep}{0.3em}
\label{tab:stats}
\begin{tabular}{l rrrrr rr}
\centering
\input{experiments/tables/statistics.tex}
\end{tabular}
\caption{Statistics.}
%\vspace{-3mm}
\end{table}

\PDComment{We probably do not need this now that we have many bugs from the case studies -- benchmarks that are not production code (e.g. multipaxos) that can be used to evaluate testing}

@@

\subsection{Stress testing vs \psharp testing}

\setlength{\tabcolsep}{.42em}
\begin{table*}[t]
\small
\centering
\begin{tabular}{l rr rrrrr}
\centering
\input{experiments/tables/results.tex}
\end{tabular}
\caption{Results.}
\label{tab:testing}
\end{table*}

@@

Controlled random scheduling has proven to be efficient for finding concurrency bugs~\cite{thomson2014sct, deligiannis2015psharp}.
